\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Jaidev Deshpande} % Your name
\address{E-12, First Floor \\ Greater Kailash 1 \\ New Delhi 110048} % Your address
\address{(+91)-844-733-5686 \\ deshpande.jaidev@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Pune} \hfill {\em July 2012} \\ 
B.E. in Electronics

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Cube26 Software Pvt Ltd}{Novemer 2015 - Present}{Data
    Scientist}{New Delhi}
\item Managing data science operations.
\item Design and deployment of server-side code for various data-driven
    applications.
\item Building deep learning models for applications in computer vision and
    NLP.
\end{rSubsection}

\begin{rSubsection}{iDataLabs}{September 2015 - December 2015}{Consultant}{New
    Delhi}
\item Developing a model for predicting marketing leads for software vendors.
\end{rSubsection}

\begin{rSubsection}{DataCulture Analytics}{January 2015 - September 2015}{Chief
    Data Scientist}{New Delhi}
\item Developing a predictive analytics platform for e-commerce and logistics
    solutions.
\item Building and maintaining a recommendation system for recommending
    logistics partners for various e-commerce companies.
\end{rSubsection}

\begin{rSubsection}{Enthought, Inc}{July 2013 - December 2015}{Scientific
    Software Developer}{Mumbai}
\item Developing automated data analysis and visualization software.
\item Core developer of the Canopy Python distribution and data analysis
    environemnt.
\item Built a continuous integration and delivery platform from scratch.
\end{rSubsection}

\begin{rSubsection}{Enthought, Inc}{April 2012 - July 2013}{Intern}{Mumbai}
\item Worked on Python tools for exploratory data analysis.
\end{rSubsection}

\begin{rSubsection}{Tata Institute of Fundamental Research}{August 2011 -
    January 2012}{Research Assistant}{Mumbai}
\item Analysis of data from various applications in material sciences and
    experimental physics.
\item Developed a system for measuring the elastic constants of solids from
    ultrasonic signals.
\end{rSubsection}

\begin{rSubsection}{University of Pune}{January 2009 - March 2012}{Research
    Assistant}{Pune}
\item Various projects in signal and image processing.
\end{rSubsection}

\end{rSection}


\begin{rSection}{Publications \& Talks}

All papers have Jaidev Deshpande as the first author.

\begin{enumerate}

\item \textit{Parameterization of Traffic Flow Using Sammon-Fuzzy Clustering} \\
    IEEE International Conference in Vehicular Electronics and Safety 2009
\item \textit{pyhht: A Python Toolbox for the Hilbert-Huang Transform} \\
    International Conference on Python in Scientific Computing, 2011, IIT Bombay
\item \textit{Mechanism Design for Evolutionary Games in Special Interest
    Groups} \\
    11th Conference of the Society of Social Choice and Welfare, Aug 2012
\item \textit{Exploratory Data Analysis with Python} \\ 
    Tutorial at the Fifth Elephant Conference on Big Data, Bangalore, July 2012
\item \textit{Fourier and Hilbert - Two Views of Nonlinear Mechanics} \\ 
    IEEE National Students Conference 2012, Pune
\item \textit{Time-Frequency Analysis with Python} \\
    International Conference on Python in Scientific Computing, 2012, IIT Bombay
\item \textit{Compressed Sensing Solvers in Python} \\
    International Conference on Python in Scientific Computing, 2013, IIT Bombay

\end{enumerate}

Several more talks and tutorial sessions on Python and data analysis delivered at various meetings.

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming languages & Python, R, MATLAB, C, Lua\\
Software development & Continuous delivery and deployment, build and test infrastructure setups\\
CI Tools & Working knowledge of Jenkins and Travis\\
Virtualization & Working knowledge of Vagrant, Packer, Virtualbox and VMWare \\
Other tools & LATEX, Mathematica, etc.
\end{tabular}

\end{rSection}


\begin{rSection}{Other Projects}
    \begin{itemize}
\item Mentor for pgmpy organization in the Google Summer of Code 2015 for projects dealing with sampling and approximate algorithms for probabilistic graphical models.
\item Co-Mentor for the scikit-learn organization in Google Summer of Code 2014 for a project dealing with linear models.
\item Mathematical modeling of centralized admission procedures (Sept 08 to Jan 09) (2nd prize in Avishkar Inter-varsity Research Festival 2009)
\item Empirical mode secomposition based feature extraction for speech recognition (Feb 10 to May 10, course requirement)
\item Analysis of empirical mode decomposition as a feature extraction method. (March 11 to Present)
\item Development of an open-source toolbox for adaptive data analysis (July 11 to Dec 11, course requirement)
\item Scikit-signal - A Python toolbox for signal processing (Jan 12 to Present)
\item PyHHT - A Python toolbox for the Hilbert-Huang Transform (Jan 12 to Present)
    \end{itemize}
\end{rSection}


\begin{rSection}{Achievements}
    \begin{itemize}
        \item Earned a distinction in the Computing for Data Analysis class
            offered by Coursera.
        \item Earned a distinction in the Data Scientist’s Toolbox class
            offered by Coursera.
        \item Semi-finalist in the ARI Atlas Shrugged Essay Contest ’09.
        \item Represented west zone in Avishkar Inter-varsity Research Festival
            2008-09, won the first prize in the Humanities category.
        \item Editor of the college magazine Lighthouse in 2008 and 2009.
        \item Held 6th position in national debate contest organized by ToI and
            the Lok-Satta Party.
    \end{itemize}
\end{rSection}

\begin{rSection}{Other Acitivities}
    \begin{itemize}
        \item Active member of the Pune, Mumbai and Delhi Python users' groups.
        \item Co-founder of a forum for scientific computing in Pune.
        \item Active member of the Ayn Rand in India intiative.
        \item Active member of the IEEE.
    \end{itemize}
\end{rSection}

\begin{rSection}{Hobbies}
    Reading, Writing, Music, Movies
\end{rSection}

\end{document}
